A holomorphic approach to membranes and fivebranes

### 2022-06-13 fivebranes/fact.tex
merge

%\documentclass[11pt]{amsart}

%\usepackage{../macros-master}
%\usepackage{macros-fivebrane}

%\begin{document}

@@

@@

As above, let $X$ be a Calabi--Yau fivefold and $S$ a real oriented one-manifold. 
In the first section we recalled a proposal for the description of the minimal twist of eleven-dimensional supergravity on $X \times S$. 
The primary object we used to describe the solutions of the equations of motion was the $\Z/2$ graded local $L_\infty$ algebra $\cL_{sugra}$, see \S \ref{s:Lsugra}. 
%As a graded vector space, observables on an open set $U \subset X \times S$ are thus $\cO(\cL_{sugra}(U)) = \Sym (\Pi \cL_{sugra})^\vee$.
%The differential is encoded by the $L_\infty$ structure which is exactly the Chevalley--Eilenberg differential. 
The $\Z/2$ graded commutative dg algebra of classical observables supported on an open set $U \subset X \times S$ is 
\[
\clie^\bu\left(\cL_{sugra}(U)\right) .
\]
We will denote the entire classical factorization algebra on $X \times S$ of classical observables by~$\clie^\bu(\cL_{sugra})$.

\parsec[s:membraneobs]

\parsec[s:fivebraneobs]

Let $Z$ be a complex threefold. 
In \ref{s:single} we have described the holomorphic twist of a theory on a single fivebrane within the (degenerate) BV formalism in terms of the (abelian) local $L_\infty$ algebra $\cL_{single}$ on $Z$. 
The factorization algebra of classical observables of the holomorphic twist of the single fivebrane theory assigns to an open set $U \subset Z$
the cochain complex
\[
\clie^\bu\left(\cL_{single}(U)\right) .
\]
We will denote the entire factorization algebra on $Z$ of classical observables by~$\clie^\bu(\cL_{single})$.

@@

\subsection{The restricted factorization algebra}

For simplicity let us consider the eleven-dimensional theory on flat space $\R \times \C^5$ with some number of fivebranes supported on
\[
0 \times 0 \times \C^3 \subset \C^5 .
\]
The general prescription of twisted holography is that (after taking into account the backreaction) the observables on a large number of fivebranes is Koszul dual to the factorization algebra

\parsec[s:flat]

%In the simple case where $Z = \C^3$ and we identify the total space of $K^{1/2}_Z \otimes \C^2$ with $\C^5$ then the manifold obtained by removing the locus of the brane is homeomorphic to
%\[
%\C^3 \times (\R \times \C^2 - 0) .
%\]
%
%Let $\pi \colon \R \times \C^5 - (0 \times \C^3) \to \C^3 \times \R_{>0}$ be the projection map whose fibers are homeomorphic to the sphere $S^4$ which links the location of the fivebranes.
%We restrict the factorization algebra of the eleven dimensional theory $\Obs_{sugra}$ to the open set obtained by removing the locus of the brane.

In the simple case that $Z = \C^3$ and we identify the total space of $K^{1/2}_Z \otimes \C^2$ with $\C^5$ there is a more direct construction of the factorization algebra $\Obs_{sugra}|_{Z}$.

Let $\pi \colon \R \times \C^5 \to \C^3$ be the projection map.
Then, via $\pi$ we can pushforward the factorization algebra associated to the eleven-dimensional theory to obtain a factorization algebra
\[
\pi_* \Obs_{sugra} 
\]
on $\C^3$.
This factorization algebra is not the factorization algebra associated to an ordinary sort of field theory on $\C^3$. 
Nevertheless there is a subfactorization algebra which admits a natural grading so that each filtered component can be understood as such.

For any open set $U \subset \C^3$ we can consider the following $\C^\times$ action on the fields of the eleven-dimensional theory supported on $\R \times \C^2 \times U$ defined by
\begin{itemize}
\item On the fields $\mu(t;w,z) \in \Omega^\bu(\R) \otimes \PV^{1,\bu}(\C^2 \times U)$ the action is
\[
\lambda \cdot \mu(t;w,z) = \mu(\lambda t;\lambda w , z).
\]
\item On the fields $\nu(t;w,z) \in \Omega^\bu(\R) \otimes \PV^{0,\bu}(\C^2 \times U)$ the action is
\[
\lambda \cdot \nu(t;w,z) = \nu(\lambda t;\lambda w , z).
\]
\item On the fields $\beta(t;w,z) \in \Omega^\bu(\R) \otimes \Omega^{0,\bu}(\C^2 \times U)$ the action is
\[
\lambda \cdot \beta(t;w,z) = \lambda^{-1} \beta(\lambda t;\lambda w , z).
\]
\item On the fields $\gamma(t;w,z) \in \Omega^\bu(\R) \otimes \Omega^{1,\bu}(\C^2 \times U)$ the action is
\[
\lambda \cdot \gamma(t;w,z) = \lambda^{-1} \gamma(\lambda t;\lambda w , z).
\]
\end{itemize}

For each $n \in \ZZ$ and open set $U \subset \C^3$, let 
\[
\pi_* \cL_{sugra}(U)^{(n)} \subset \cL_{sugra}(\R \times \C^2 \times U)
\]
be the weight $n$ eigenspace with respect to this $\C^\times$ action. 
The $\C^\times$ action is compatible with the $\Z/2$ graded $L_\infty$ structure on $\cL_{sugra}$. 
Since the $n$th eigenspace is trivial when $n < -1$, we see that the product
\[
(\Bar{\pi}_* \cL_{sugra})(U) \define \prod_{n \geq -1} (\pi_*\cL_{sugra})(U)^{(n)}
\]
is equipped with the structure of a $\Z/2$ graded $L_\infty$ algebra.
In this way, the assignment 
\[
\Bar{\pi}_* \cL_{sugra} \colon U \mapsto (\Bar{\pi}_* \cL_{sugra})(U) 
\]
defines a sheaf of $\Z/2$ graded $L_\infty$ algebras on $\C^3$.

As an example, let us consider the weight $(-1)$ piece of the decomposition $\Omega^{0,\bu}(Z, \cV^{(-1)})$. 
We will show that 
\[
\cV^{(-1)} = K^{-1/2}_Z \otimes \C^2 \oplus \cO_Z \oplus \Pi \T^*_Z 
\]
whose Dolbeault forms are equipped with the $\dbar$ operator and the $\del$ operator which takes functions to one-forms.

Explicitly weight zero summand $\cV^{(0)}$ consists of:
\begin{itemize}
\item 
Vector fields which are locally of the form $f^a(z) \del_{w_a}$ where $f^{a}(z)$ is a holomorphic function on $\C^3$.
Notice that these vector fields are automatically divergence-free.
Since $\del_{w_a}$ is treated as a section of $K^{-1/2}_Z$ we see that these are local sections of $K^{-1/2}_Z \otimes \C^2$. 
\item 
Next there are holomorphic functions (type $\beta$) and holomorphic $one$-forms (type $\gamma$) which do not depend on $w_a$. 
Since $\del$ is weight zero for the decomposition these forms combine to form the $\Z/2$ graded complex of sheaves
\[
\cO_Z \xto{\del} \Pi \Omega^{1,hol}_Z .
\]
\end{itemize}

As a holomorphic vector bundle, we will see that
\[
\cV^{(0)} = \T_Z \oplus \lie{sl}(2) \otimes \cO_Z \oplus \Pi \left( \T^*_Z \otimes K^{-1/2}_Z \otimes \C^2 \right).
\]
The $L_\infty$ structure of $\cL_{sugra}$ endows the sheaf of sections of this holomorphic vector bundle with a Lie bracket which we will describe.

Explicitly, we enumerate all weight zero holomorphic sections:
\begin{itemize}
\item Vector fields which are locally of the form $\mu = f^i(z) \del_{z_i}$ or $\mu = g(z) A^{ab} w_a \del_{w_b}$ where $(A^{ab}) \in \lie{sl}(2)$.
\item Holomorphic functions of the form $\beta = w_a f(z)$ and holomorphic one-forms of the form $\gamma = g^{a}(z) \d w_a + h^{a} (z) w_a \d z$. 
Since $\del$ is weight zero, such sections are equipped with a differential 
\[
\Gamma^{hol}(Z, K^{1/2}) \xto{D} \Pi \Gamma^{hol}(Z, K^{1/2}) \oplus \Pi\Omega^{1,hol}(Z, K^{1/2}) 
\]
which sends $w_a f(z) \mapsto (f(z) , w_a \del f (z))$. 
The $\Z/2$ graded complex of sheaves is clearly equivalent to $\Pi\Omega^{1,hol}(Z, K^{1/2})$. 
\end{itemize}

\parsec[s:??]

\parsec[s:e36]
The exceptional super Lie algebra $E(3|6)$

Let $Z$ be a complex manifold of complex dimension three equipped with a square-root of the canonical bundle.
To freely resolve the space of holomorphic sections
we employ the Dolbeault complex of the appropriate holomorphic vector bundle. 
For holomorphic vector fields we introduce the dg Lie algebra
\[
\Omega^{0,\bu}(X , \T_X)
\]
of $(0,\bu)$ Dolbeault forms with values in the holomorphic tangent bundle. 
Also, for any holomorphic vector bundle $V$ let
\[
\Omega^{-1/2 , \bu}(X, V) = \Omega^{0,\bu}(X , V \otimes \T_X^* \otimes \sigma^{-1}) .
\]

\parsec

We define a super dg Lie algebra to be a $\Z \times \Z/2$ graded Lie algebra $\fg = \fg_+^\bu \oplus \Pi \fg_-^\bu$ which satisfies totalized graded skew symmetry and is equipped with a differential $\d$ of bidegree $(1,+)$ that is square zero and a derivation for the bracket. 
For more details see \cite[Section 2]{EHSW}.

\begin{dfn}
Let $\sigma$ and $P$ be as above. 
Define the following local super Lie algebra $\cE_{P,\sigma}$ on $X$ whose even and odd parts are
\begin{align*}
\cE_{P,\sigma,+} & = \Omega^{0,\bu}(X , \T_X) \oplus \Omega^{0,\bu}(X , \ad P)\\
\cE_{P,\sigma,-} & = \Omega^{1 , \bu}(X, R_X \otimes \sigma^{-1}) .
\end{align*}
The differential is given by the natural $\dbar$-operator whenever it makes sense.
The bracket is defined analogously as in formulas \brian{ref}. 
\end{dfn}

On $X = \C^3$ there is a natural choice for $\sigma = K^{1/2}_{\CC^3}$, and we can take $P$ to be the trivial $SL(2)$ bundle. 
With these choices we have the following easy lemma.

%\end{document}

>>>>

\documentclass[11pt]{amsart}

%\usepackage{../macros-master}
\usepackage{macros-fivebrane}

\begin{document}

@@

In this section we consider the classical factorization algebra of observables of our prototype for the holomorphic twist of eleven-dimensional supergravity.

@@

As above, let $X$ be a Calabi--Yau fivefold and $S$ a real oriented one-manifold. 
In the first section we recalled a proposal for the description of the minimal twist of eleven-dimensional supergravity on $S \times X$. 
The primary object we used to describe the solutions of the equations of motion was the $\Z/2$ graded local $L_\infty$ algebra $\cL_{sugra}$, see \S \ref{s:Lsugra}. 
%As a graded vector space, observables on an open set $U \subset X \times S$ are thus $\cO(\cL_{sugra}(U)) = \Sym (\Pi \cL_{sugra})^\vee$.
%The differential is encoded by the $L_\infty$ structure which is exactly the Chevalley--Eilenberg differential.

The $\Z/2$ graded commutative dg algebra of classical observables supported on an open set $U \subset X \times S$ is 
\[
\clie^\bu\left(\cL_{sugra}(U)\right) .
\]
We will denote the entire classical factorization algebra on $X \times S$ of classical observables by~$\clie^\bu(\cL_{sugra})$.

%\parsec[s:membraneobs]
%
%
%\parsec[s:fivebraneobs]
%
%Let $Z$ be a complex threefold. 
%In \ref{s:single} we have described the holomorphic twist of a theory on a single fivebrane within the (degenerate) BV formalism in terms of the (abelian) local $L_\infty$ algebra $\cL_{single}$ on $Z$. 
%The factorization algebra of classical observables of the holomorphic twist of the single fivebrane theory assigns to an open set $U \subset Z$
%the cochain complex
%\[
%\clie^\bu\left(\cL_{single}(U)\right) .
%\]
%We will denote the entire factorization algebra on $Z$ of classical observables by~$\clie^\bu(\cL_{single})$.

\parsec[s:restricted]

With an eye towards holography for fivebranes we fix a complex three-fold $Z$ where the fivebranes will be supported and consider the eleven-dimensional theory on $\R \times X_Z$ where $X_Z$ is the Calabi--Yau fivefold
\[
X_Z = \text{Tot}(K_Z^{1/2} \otimes \C^2),
\]
the total space of the rank two bundle $K_Z^{1/2} \otimes \C^2$ over $Z$. 
Here the holomorphic volume form
One can also think about $\R \times X_Z$ as the total space of the {\em real} rank five bundle over $Z$; although this description obfuscates the geometric structure used to define the eleven-dimensional theory.
Let 
\[
\pi \colon \R \times X_Z \to Z 
\]
be the map which projects out the real factor followed by the projection to the base of the total space of the complex rank two bundle $p \colon X_Z \to Z$.

Like sheaves, factorization algebras can be pushed forward; thus from the factorization algebra $\Obs_{sugra}$ on $\R \times X_Z$ we obtain a factorization algebra $\pi_* \Obs_{sugra}$ on $Z$. 
To an open set $U \subset Z$ the value of this factorization algebra is
\begin{align*}
(\pi_* \Obs_{sugra}) (U) & = \Obs_{sugra} \left(\pi^{-1} U\right) \\
& = \Obs_{sugra}(\R \times p^{-1}U) .
\end{align*}

This factorization algebra is not the factorization algebra associated to an ordinary sort of field theory on $Z$.
Nevertheless there is a subfactorization algebra which admits a natural grading so that each filtered component can be understood as such.
This grading is determined by a $\C^\times$ action on the fields of the eleven-dimensional theory on $\R \times X_Z$ which we now describe.

\parsec[s:gradingfivebrane]

In a local chart $U \subset Z$ we can write a generic field of the eleven-dimensional theory on $\pi^{-1} U$ in coordinates as $f(t;w,z)$ where $t \in \R$ is the real coordinate, $w=(w_1,w_2)$ is the holomorphic fiber coordinate of the rank two bundle $X_Z$ over $Z$, and $z = (z_1,z_2,z_3)$ is a local holomorphic coordinate for $U \subset Z$.

%For simplicity let us consider the eleven-dimensional theory on flat space $\R \times \C^5$ with some number of fivebranes supported on
%\[
%0 \times 0 \times \C^3 \subset \C^5 .
%\]
%is that (after taking into account the backreaction) the observables on a large number of fivebranes is Koszul dual to the factorization algebra 
%
%\parsec[s:flatdecomp]
%
%%In the simple case where $Z = \C^3$ and we identify the total space of $K^{1/2}_Z \otimes \C^2$ with $\C^5$ then the manifold obtained by removing the locus of the brane is homeomorphic to
%%\[
%%\C^3 \times (\R \times \C^2 - 0) .
%%\]
%%
%%Let $\pi \colon \R \times \C^5 - (0 \times \C^3) \to \C^3 \times \R_{>0}$ be the projection map whose fibers are homeomorphic to the sphere $S^4$ which links the location of the fivebranes.
%%We restrict the factorization algebra of the eleven dimensional theory $\Obs_{sugra}$ to the open set obtained by removing the locus of the brane.
%
%In the simple case that $Z = \C^3$ and we identify the total space of $K^{1/2}_Z \otimes \C^2$ with $\C^5$ there is a more direct construction of the factorization algebra $\Obs_{sugra}|_{Z}$. 
%
%Let $\pi \colon \R \times \C^5 \to \C^3$ be the projection map.
%Then, via $\pi$ we can pushforward the factorization algebra associated to the eleven-dimensional theory to obtain a factorization algebra
%\[
%\pi_* \Obs_{sugra} 
%\]
%on $\C^3$.
%This factorization algebra is not the factorization algebra associated to an ordinary sort of field theory on $\C^3$. 
%Nevertheless there is a subfactorization algebra which admits a natural grading so that each filtered component can be understood as such.

With this notation in place, we introduce the following $\C^\times$ action on the fields of the eleven-dimensional theory:
\begin{itemize}
\item On the fields $\mu(t;w,z) \in \Omega^\bu(\R) \otimes \PV^{1,\bu}(\C^2 \times U)$ the action is
\[
\lambda \cdot \mu(t;w,z) = \mu(\lambda t;\lambda w , z).
\]
\item On the fields $\nu(t;w,z) \in \Omega^\bu(\R) \otimes \PV^{0,\bu}(\C^2 \times U)$ the action is
\[
\lambda \cdot \nu(t;w,z) = \nu(\lambda t;\lambda w , z).
\]
\item On the fields $\beta(t;w,z) \in \Omega^\bu(\R) \otimes \Omega^{0,\bu}(\C^2 \times U)$ the action is
\[
\lambda \cdot \beta(t;w,z) = \lambda^{-1} \beta(\lambda t;\lambda w , z).
\]
\item On the fields $\gamma(t;w,z) \in \Omega^\bu(\R) \otimes \Omega^{1,\bu}(\C^2 \times U)$ the action is
\[
\lambda \cdot \gamma(t;w,z) = \lambda^{-1} \gamma(\lambda t;\lambda w , z).
\]
\end{itemize}

The main result of this section is the following.

\begin{prop}
\end{prop}

For each $n \in \ZZ$ and open set $U \subset \C^3$, let 
\[
\pi_* \cL_{sugra}(U)^{(n)} \subset \cL_{sugra}(\pi^{-1} U)
\]
be the weight $n$ eigenspace with respect to this $\C^\times$ action. 
The $\C^\times$ action is compatible with the $\Z/2$ graded $L_\infty$ structure on $\cL_{sugra}$. 
Since the $n$th eigenspace is trivial when $n < -1$, we see that the product
\[
(\Bar{\pi}_* \cL_{sugra})(U) \define \prod_{n \geq -1} (\pi_*\cL_{sugra})(U)^{(n)}
\]
is equipped with the structure of a $\Z/2$ graded $L_\infty$ algebra.
In this way, the assignment 
\[
\Bar{\pi}_* \cL_{sugra} \colon U \mapsto (\Bar{\pi}_* \cL_{sugra})(U) 
\]
defines a sheaf of $\Z/2$ graded $L_\infty$ algebras on $\C^3$.

We explicitly describe the first homogenous weights of $\Bar{\pi}_* \cL_{sugra}$.

As an example, let us consider the weight $(-1)$ piece of the decomposition $\Omega^{0,\bu}(Z, \cV^{(-1)})$. 
We will show that 
\[
\cV^{(-1)} = K^{1/2}_Z \otimes \C^2 \oplus \cO_Z \oplus \Pi \T^*_Z 
\]
whose Dolbeault forms are equipped with the $\dbar$ operator and the $\del$ operator which takes functions to one-forms.

Explicitly weight zero summand $\cV^{(0)}$ consists of:
\begin{itemize}
\item 
Vector fields which are locally of the form $f^a(z) \del_{w_a}$ where $f^{a}(z)$ is a holomorphic function on $\C^3$.
Notice that these vector fields are automatically divergence-free.
Since $\del_{w_a}$ is treated as a section of $K^{1/2}_Z$ we see that these are local sections of $K^{1/2}_Z \otimes \C^2$. 
\item 
Next there are holomorphic functions (type $\beta$) and holomorphic $one$-forms (type $\gamma$) which do not depend on $w_a$. 
Since $\del$ is weight zero for the decomposition these forms combine to form the $\Z/2$ graded complex of sheaves
\[
\cO_Z \xto{\del} \Pi \Omega^{1,hol}_Z .
\]
\end{itemize}

As a holomorphic vector bundle, we will see that $\cV^{(0)}$ is 
\[
\cV^{(0)} = \T_Z \oplus \lie{sl}(2) \otimes \cO_Z \oplus \Pi \left( \T^*_Z \otimes K^{-1/2}_Z \otimes \C^2 \right).
\]
The $L_\infty$ structure of $\cL_{sugra}$ endows the sheaf of sections of this holomorphic vector bundle with a Lie bracket which we will describe.

Explicitly, we enumerate all weight zero holomorphic sections:
\begin{itemize}
\item Vector fields which are locally of the form 
\[
\mu = f^i(z) \del_{z_i} - \frac12 \del_{z_i} f^i(z) w_a \del_{w_a}
\]
and vector fields which are locally of the form
\[
\mu = g(z) A^{ab} w_a \del_{w_b}.
\]
The condition that $\mu$ be divergence-free implies that $(A^{ab}) \in \lie{sl}(2)$.
We will identify the first such vector fields with sections of $\T_Z$ and the second such vector fields with sections of $\lie{sl}(2) \otimes \cO_Z$. 
\item Holomorphic functions of the form $\beta = w_a f(z)$ and holomorphic one-forms of the form $\gamma = g^{a}(z) \d w_a + h^{a} (z) w_a \d z$. 
Since $\del$ is weight zero, such sections are equipped with a differential 
\[
\Gamma^{hol}(Z, K^{-1/2}) \xto{D} \Pi \Gamma^{hol}(Z, K^{-1/2}) \oplus \Pi\Omega^{1,hol}(Z, K^{-1/2}) 
\]
which sends $w_a f(z) \mapsto (f(z) , w_a \del f (z))$. 
This $\Z/2$ graded complex of sheaves is clearly equivalent to $\Pi\Omega^{1,hol}(Z, K^{-1/2})$. 
\end{itemize}

The $L_\infty$ structure on $\Bar{\pi}_* \cL_{sugra}$ induces the structure of a local $\Z/2$ graded dg Lie algebra on $\Omega^{0,\bu}(Z, \cV^{(0)})$. 
The differential is simply $\dbar$. 
The Lie bracket is induced from a Lie algebra structure on holomorphic sections of $\cV^{(0)}$ which we can describe as follows:
\begin{itemize}
\item For $\Vect^{hol}(Z)$ there is the standard commutator of holomorphic vector fields. 
This acts on the sections of $\lie{sl}(2) \otimes \cO_Z$ and $\Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2)$ by Lie derivative. 
\item On sections of $\lie{sl}(2) \otimes \cO_Z$ there is the matrix commutator. 
This acts on the odd part $\Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2)$ where we view $\C^2$ as the fundamental $\lie{sl}(2)$ representation. 
\item Finally, and most interestingly, there is a bracket of the form
\[
\Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2) \times \Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2) \to \Vect^{hol}(Z) \oplus \lie{sl}(2) \otimes \cO_Z 
\]
given in coordinates by
\[
[f^a(z) \d w_a , g^a \d w_b] = \left(??, ??\right).
\]
\end{itemize}

\parsec[s:mainfact]

@@

\end{document}
